### 2015-05-13 evaluation.tex
update in evaluation text

@@

We can notice that \whoop is significantly faster than \corral. This is expected as \whoop achieves scalability using over-approximation and summarization techniques. This allows \whoop to perform especially well in complex drivers such as the r8169 ethernet driver: although \corral ... and timeouts with a csb of 9, \whoop manages to analyze the driver in 228.1 seconds. We believe that the reason behind this is that r8169 has many loops and uses deeply-nested recursion in some entry points, which \corral might not be able to handle efficiently.

>>>>

We can notice that \whoop is significantly faster than \corral. This is expected as \whoop achieves scalability using over-approximation. For example, \corral timeouts in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze r8169 in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some of its entry points, which might get \corral stuck.

@@
